% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{pslatex} % Times New Roman
%\renewcommand{\rmdefault}{phv} % Arial
%\renewcommand{\sfdefault}{phv} % Arial
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Yu Usami}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{2-43-3 Sendagi Bunkyo-ku \#502, Tokyo, Japan}
 \moveleft.5\hoffset\centerline{+8190-9663-8160}
 \moveleft.5\hoffset\centerline{yusmi@is.s.u-tokyo.ac.jp}
 \moveleft.5\hoffset\centerline{http://yusmi.org/}


\begin{resume}
 
\section{Research \\ Interests}
Natural Language Processing, Machine Learning, Semantics.\\

\section{Education}
\textbf{M.S., Computer Science} \hfill April 2011 -- current\\
University of Tokyo, Tokyo, Japan\\
Supervisor: Akiko Aizawa\\
Expected completion: March 2013

\textbf{B.S., Information Science} \hfill April 2006 -- March 2011\\
University of Tokyo, Tokyo, Japan\\
Thesis: \textit{Named Entity Recognition Trained on Automatically Created Huge Data}\\
Supervisor: Jun'ichi Tsujii\\

\section{Research \\ Experience}
\textbf{Research Intern}, Mentor: Satoshi Sekine \hfill August 2011 -- October 2011\\
Rakuten Institute of Technology, New York, NY, USA\\
Work on attribute-value pair extraction from product descriptions. 

\textbf{Research Assistant}, Supervisor: Akiko Aizawa \hfill May 2011 -- July 2011\\
National Institute of of Informatics, Tokyo, Japan\\
Work on mathematical expression extraction from papers.

\textbf{Directed Research}, Supervisor: Jun'ichi Tsujii \hfill October 2011 -- March 2011\\
University of Tokyo, Tokyo, Japan\\
Work on gene and protein names recognition from biomedicine text.\\

\section{Publications}
\textbf{Yu Usami}, Han-Cheol Cho, Naoaki Okazaki, and Jun'ichi Tsujii. Automatic Acquisition of Huge Training Data for Bio-Medical Named Entity Recognition. 
In \textit{Proceedings of BioNLP 2011 Workshop}, pages 65-73, Portland, Oregon, USA, June 2011.

\textbf{Yu Usami}, Han-Cheol Cho, Naoaki Okazaki, and Jun'ichi Tsujii. Automatic Acquisition of Huge Training Data for Named Entity Recognition.
\textit{Technical Report (Information Processing Society of Japan, SIGNL201)}. pages 1-8, May 2011. (in Japanese).

\textbf{Yu Usami}, Han-Cheol Cho, Naoaki Okazaki, and Jun'ichi Tsujii. Named Entity Recognition Trained on Automatically Created Huge Data.
In \textit{Proceedings of the 17th Japan Natural Language Processing Conference}. March 2011. (in Japanese).\\

\section{Work \\ Experience}
\textbf{Part-time Engineer} \hfill September 2010 -- July 2011\\
DeNA Co. Ltd., Tokyo, Japan\\
Work on social game applications and debugging tools development.

\textbf{Part-time Engineer} \hfill November 2008 -- April 2010\\
Realglobe Inc., Tokyo, Japan\\
Work on web applications development.\\

\section{Activities}
\textbf{Co-Organizer:} {\sl Speech and Language Processing (Daniel Jurafsky and James H. Martin)} Reading Group \hfill October 2010 -- December 2010

\textbf{Organizer:} {\sl Pattern Recognition and Machine Learning (Christopher M. Bishop)} Reading Group \hfill April 2011 -- current

\textbf{Co-Organizer:} {\sl Foundations of Statistical Natural Language Processing (Chris Manning and Hinrich Schütze)} Reading Group \hfill April 2011 -- June 2011\\


\section{Computer \\ Skills}
\textit{Programming Languages:} C/C++, Python, JavaScript, Clojure, Ruby, Java, Perl \\
\textit{Platforms:} CentOS, Linux, Mac OS X\\

\section{Languages}
Native Japanese speaker.\\
Good at English. TOEIC score 750 (October 2010), and TOEFL score 72 (May 2010). \\

\section{References} 
Dr. Jun'ichi Tsujii \\
Microsoft Research Asia, Beijing, China

Prof. Akiko Aizawa \\
National Institute of Informatics, Tokyo, Japan

Prof. Satoshi Sekine \\
New York University, New York, NY, USA
\end{resume}
\end{document}




